Notebook

### 2022-03-05 doc/notebook/notebook.Rmd
Minor edit to code for length:weight plot

```{r frog-lenth-weight-plot, echo=FALSE}
read_csv(here::here("data", "clean", "frog_translocation.csv")) %>% 
ggplot(aes(x = log10(length), y = log10(weight))) +
  geom_point() +
  geom_smooth(method = lm)
plot
```

>>>>

```{r frog-lenth-weight-plot, echo=FALSE}
read_csv(here::here("data", "clean", "frog_translocation.csv")) %>% 
ggplot(aes(x = log10(length), y = log10(weight))) +
  geom_point() +
  geom_smooth(method = "lm")
plot
```
